### 2015-02-22 fundamentals/examples.tex
swap capability and ecosystem in III

The success of the \Cyclus simulator can be measured in many ways.
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development
model and of fundamental simulation capability. Nascent promising growth of the \Cyclus
ecosystem at multiple institutions indicates that a fuel cycle simulator can
advance in this community-driven development paradigm. Additionally, simulation
results for both once-through and more complex recycling scenarios demonstrate that
\Cyclus possesses the fundamental fuel cycle simulation capabilities to
contribute to the field.

>>>>

The success of the \Cyclus simulator can be measured in many ways.  The most
compelling are demonstrations of fundamental simulation capability and of the
feasibility of the \Cyclus community-driven development model. Nascent promising
growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
cycle simulator can advance in this community-driven development
paradigm. Additionally, simulation results for both once-through and more
complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
fuel cycle simulation capabilities to contribute to the field.
